Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-03-29 analysis/paper/paper.qmd
Minor spelling change

```{r}
#| label: fig-tcsa-size
#| fig-cap: "Artifact size and TSCA values by lithic raw material"
#| fig-height:  3.5

@@

According to the different weapon-delivery systems that can be inferred from TCSA values, the majority of stemmed points from the Korean Palaeolithic were probably used as javelin tips and stabbing spear tips. In general, though, we noted a wide range and also differing distributions of TCSA values in each assemblage. Therefore, we conclude that stemmed points served diverse and not highly patterned roles during the Late Paleolithic. Prior to the LGM, people may have encountered unfamiliar situations and use stemmed points as a multifunctional tool to carry out multiple tasks. During the LGM and following we find production and discard of stemmed points declined, but their ballistic properties remained largely unchanged. Considering that many of our predictions about TCSA were not supported by the data, we speculate that the ballistic aspects of stemmed points were not highly sensitive to global climate dynamics and local geographic variation, but instead were optimal for the wide range of conditions encountered by people during the Late Palaeolithic in Korea.

>>>>

```{r}
#| label: fig-tcsa-size
#| fig-cap: "Artifact size and TCSA values by lithic raw material"
#| fig-height:  3.5

@@

According to the different weapon-delivery systems that can be inferred from TCSA values, the majority of stemmed points from the Korean Paleolithic were probably used as javelin tips and stabbing spear tips. In general, though, we noted a wide range and also differing distributions of TCSA values in each assemblage. Therefore, we conclude that stemmed points served diverse and not highly patterned roles during the Late Paleolithic. Prior to the LGM, people may have encountered unfamiliar situations and use stemmed points as a multifunctional tool to carry out multiple tasks. During the LGM and following we find production and discard of stemmed points declined, but their ballistic properties remained largely unchanged. Considering that many of our predictions about TCSA were not supported by the data, we speculate that the ballistic aspects of stemmed points were not highly sensitive to global climate dynamics and local geographic variation, but instead were optimal for the wide range of conditions encountered by people during the Late Palaeolithic in Korea.
